\documentclass{article}
\title{}
\author{}
\date{}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{tabularx}

\begin{document}
Language: Swift

EventKit / EKStructuredLocation

Class

\textbf{EKStructuredLocation}

A class that specifies a geofence to activate the alarm of a calendar item.

iOS 6.0+ | iPadOS 6.0+ | Mac Catalyst 13.1+ | macOS 10.8+ | visionOS 1.0+ | watchOS 2.0+

\texttt{class EKStructuredLocation}

Overview

Use \texttt{init(title:)} to create a new structured location, then set it to the \texttt{structuredLocation} property of an \texttt{EKAlarm} object.

Topics

Creating Structured Locations

\texttt{convenience init(title: String)}

Creates a new structured location with the specified title.

\texttt{convenience init(mapItem: MKMapItem)}

Creates a new structured location with the specified map item.

Accessing Structured Location Properties

\texttt{var title: String?}

The title of the location.

\texttt{var geoLocation: CLLocation?}

The core location.

\texttt{var radius: Double}

A minimum distance from the core location that would trigger the alarm or reminder.

Relationships

Inherits From

\texttt{EKObject}

Conforms To

\texttt{CVarArg}

\texttt{CustomDebugStringConvertible}

\texttt{CustomStringConvertible}

\texttt{Equatable}

\texttt{Hashable}

\texttt{NSCopying}

\texttt{NSObjectProtocol}

See Also

Alarms

Setting an alarm

Alert users of events and reminders with an alarm.

\texttt{class EKAlarm}

A class that represents an alarm.

Developer Documentation

Platforms | Topics \& Technologies | Resources | Programs
---|---|---|---
iOS | Accessibility | Documentation | Apple Developer Program
iPadOS | Accessories | Tutorials | Apple Developer Enterprise Program
macOS | App Extension | Downloads | App Store Small Business Program
tvOS | App Store | Forums | MFi Program
visionOS | Audio \& Video | Videos | News Partner Program
watchOS | Augmented Reality | Support | Video Partner Program
Tools | Design | Support Articles | Security Bounty Program
Swift | Distribution | Contact Us | Security Research Device Program
SwiftUI | Education | Bug Reporting |
Swift Playground | Fonts | System Status | Events
TestFlight | Games | Account | Meet with Apple
Xcode | Health \& Fitness | Apple Developer | Apple Developer Centers
Xcode Cloud | In-App Purchase | App Store Connect | App Store Awards
SF Symbols | Localization | Certificates, IDs, \& Profiles | Apple Design Awards
| Maps \& Location | Feedback Assistant | Apple Developer Academies
| Machine Learning | | WWDC
| Open Source | |
| Security | |
| Safari \& Web | |

To submit feedback on documentation, visit Feedback Assistant.

Copyright \copyright\ 2025 Apple Inc. All rights reserved. Terms of Use Privacy Policy Agreements and Guidelines

\newpage
\end{document}