\documentclass{article}
\title{}
\author{}
\date{}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{tabularx}

\begin{document}
Language: \textit{Swift}

EventKit / EKAlarm

Class

\textbf{EKAlarm}

A class that represents an alarm.

iOS 4.0+ | iPadOS 4.0+ | Mac Catalyst 13.1+ | macOS 10.8+ | visionOS 1.0+ | watchOS 2.0+

\texttt{class EKAlarm}

\textbf{Overview}

An \texttt{EKAlarm} object represents an alarm in Event Kit. Use the \texttt{init(absoluteDate:)} and \texttt{init(relativeOffset:)} class methods to create an alarm and use the properties to set information about an alarm. In macOS Mountain Lion, you can specify an action to trigger when the alarm fires via the \texttt{emailAddress}, \texttt{soundName}, or \texttt{url} property.

\textbf{Topics}

\textbf{Creating an Alarm}

\texttt{init(absoluteDate: Date)}

Creates and returns an alarm with an absolute date.

\texttt{init(relativeOffset: TimeInterval)}

Creates and returns an alarm with a relative offset.

\textbf{Accessing Alarm Dates}

\texttt{var absoluteDate: Date?}

The absolute date for the alarm.

\texttt{var relativeOffset: TimeInterval}

The offset from the start of an event, at which the alarm fires.

\textbf{Setting GeoFence-based Alarms}

\texttt{enum EKAlarmProximity}

A value indicating whether an alarm is triggered by entering or exiting a region.

\texttt{var proximity: EKAlarmProximity}

A value indicating how a location-based alarm is triggered.

\texttt{var structuredLocation: EKStructuredLocation?}

The location to trigger an alarm.

\textbf{Triggering Alarm Actions}

These properties are only available in macOS 10.8 or later.

\texttt{enum EKAlarmType}

A value that specifies what type of action occurs when the alarm triggers.

\texttt{var type: EKAlarmType}

The type of action to trigger when the alarm fires.

\texttt{var emailAddress: String?}

The recipient of an email to send when the alarm triggers.

\texttt{var soundName: String?}

The name of the sound to play when the alarm triggers.

\textbf{Relationships}

\textbf{Inherits From}

\textit{EKObject}

\textbf{Conforms To}

\textit{CVarArg}

\textit{CustomDebugStringConvertible}

\textit{CustomStringConvertible}

\textit{Equatable}

\textit{Hashable}

\textit{NSCopying}

\textit{NSObjectProtocol}

\textbf{See Also}

\textbf{Alarms}

\textit{Setting an alarm}

Alert users of events and reminders with an alarm.

\texttt{class EKStructuredLocation}

A class that specifies a geofence to activate the alarm of a calendar item.

Developer Documentation

Platforms & Topics \& Technologies & Resources & Programs \\
iOS & Accessibility & Documentation & Apple Developer Program \\
iPadOS & Accessories & Tutorials & Apple Developer Enterprise Program \\
macOS & App Extension & Downloads & App Store Small Business Program \\
tvOS & App Store & Forums & MFi Program \\
visionOS & Audio \& Video & Videos & News Partner Program \\
watchOS & Augmented Reality & Support & Video Partner Program \\
Tools & Design & Support Articles & Security Bounty Program \\
Swift & Distribution & Contact Us & Security Research Device Program \\
SwiftUl & Education & Bug Reporting & Events \\
Swift Playground & Fonts & System Status & Meet with Apple \\
TestFlight & Games & Account & Apple Developer Centers \\
Xcode & Health \& Fitness & Apple Developer & App Store Awards \\
Xcode Cloud & In-App Purchase & App Store Connect & Apple Design Awards \\
SF Symbols & Localization & Certificates, IDs, \& Profiles & Apple Developer Academies \\
& Maps \& Location & Feedback Assistant & WWDC \\
& Machine Learning & & \\
& Open Source & & \\
& Security & & \\
& Safari \& Web & & \\

To submit feedback on documentation, visit Feedback Assistant.

Light Dark Auto

Copyright \copyright 2025 Apple Inc. All rights reserved. Terms of Use Privacy Policy Agreements and Guidelines

\newpage
\end{document}