\documentclass{article}
\title{}
\author{}
\date{}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{tabularx}

\begin{document}
EventKit / EKSource

Class

\textbf{EKSource}

An abstract superclass that represents the account a calendar belongs to.

iOS 5.0+ | iPadOS 5.0+ | Mac Catalyst 13.1+ | macOS 10.8+ | visionOS 1.0+ | watchOS 2.0+

\texttt{class EKSource}

Overview

You do not create instances of this class; instead, you retrieve EKSource objects from an \texttt{EKEventStore}
object. Use the \texttt{sources} property to get all the EKSource objects for an event store, and use the methods in this
class to access properties of the source object.

Topics

Accessing Source Properties

\texttt{enum EKSourceType}

The type of source object.

\texttt{var sourceIdentifier: String}

A unique identifier for the source object.

\texttt{var sourceType: EKSourceType}

The type of this source object.

\texttt{var title: String}

The name of this source object.

Accessing Calendars

\texttt{func calendars(for: EKEntityType) -> Set<EKCalendar>}

Returns the calendars that belong to this source object that support a particular entity type.

\texttt{var calendars: Set<EKCalendar>}

The calendars that belong to this source object.

Deprecated

Entity Type

\texttt{enum EKEntityType}

The type of entities allowed for a source.

Instance Properties

\texttt{var isDelegate: Bool}

Relationships

Inherits From

\texttt{EKObject}

Conforms To

\texttt{CVarArg}

\texttt{CustomDebugStringConvertible}

\texttt{CustomStringConvertible}

\texttt{Equatable}

\texttt{Hashable}

\texttt{NSObjectProtocol}

See Also

Common objects

\texttt{class EKCalendarItem}

An abstract superclass for calendar events and reminders.

\texttt{class EKObject}

An abstract superclass for all EventKit classes that have persistent instances.

\newpage
\end{document}