\documentclass{article}
\title{}
\author{}
\date{}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{tabularx}

\begin{document}
EventKit / EKSource

Class

\textbf{EKSource}

An abstract superclass that represents the account a calendar belongs to.

iOS 5.0+ | iPadOS 5.0+ | Mac Catalyst 13.1+ | macOS 10.8+ | visionOS 1.0+ | watchOS 2.0+

\texttt{@interface EKSource : EKObject}

Overview

You do not create instances of this class; instead, you retrieve \texttt{EKSource} objects from an \texttt{EKEventStore} object. Use the \texttt{sources} property to get all the \texttt{EKSource} objects for an event store, and use the methods in this class to access properties of the source object.

Topics

Accessing Source Properties

\texttt{EKSourceType}

The type of source object.

\texttt{sourceIdentifier}

A unique identifier for the source object.

\texttt{sourceType}

The type of this source object.

\texttt{title}

The name of this source object.

Accessing Calendars

\texttt{- calendarsForEntityType:}

Returns the calendars that belong to this source object that support a particular entity type.

\texttt{calendars}

The calendars that belong to this source object.

\textit{Deprecated}

Entity Type

\texttt{EKEntityType}

The type of entities allowed for a source.

Instance Properties

\texttt{isDelegate}

Relationships

Inherits From

\texttt{EKObject}

See Also

Common objects

\texttt{EKCalendarItem}

An abstract superclass for calendar events and reminders.

\texttt{EKObject}

An abstract superclass for all EventKit classes that have persistent instances.

\newpage
\end{document}