\documentclass{article}
\title{}
\author{}
\date{}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{tabularx}

\begin{document}
EventKit/EKError

Structure

\textbf{EKError}

An EventKit error.

iOS | iPadOS | Mac Catalyst | macOS | visionOS | watchOS

\texttt{struct EKError}

Topics

Error Codes

\texttt{static var eventNotMutable: EKError.Code}

The event isn't mutable and you can't save or delete it.

\texttt{static var noCalendar: EKError.Code}

The event isn't associated with a calendar.

\texttt{static var noEndDate: EKError.Code}

The event has no start date set.

\texttt{static var noStartDate: EKError.Code}

The event has no end date set.

\texttt{static var datesInverted: EKError.Code}

The event's end date occurs before its start date.

\texttt{static var internalFailure: EKError.Code}

An internal error occurred.

\texttt{static var calendarReadOnly: EKError.Code}

The calendar is read-only and you can't add events to it.

\texttt{static var durationGreaterThanRecurrence: EKError.Code}

The duration of an event is greater than its recurrence interval.

\texttt{static var alarmGreaterThanRecurrence: EKError.Code}

The alarm interval is greater than the recurrence interval.

\texttt{static var startDateTooFarInFuture: EKError.Code}

The start date is further into the future than the calendar can display.

\texttt{static var startDateCollidesWithOtherOccurrence: EKError.Code}

The event's start date collides with another occurrence of the event.

\texttt{static var objectBelongsToDifferentStore: EKError.Code}

The object belongs to a different calendar store.

\texttt{static var invitesCannotBeMoved: EKError.Code}

You can't move the event because it's an invitation.

\texttt{static var invalidSpan: EKError.Code}

The system encountered an invalid span during a save or deletion.

\texttt{static var calendarHasNoSource: EKError.Code}

You can't save the calendar without setting a source first.

\texttt{static var calendarSourceCannotBeModified: EKError.Code}

You can't move the calendar to another source.

\texttt{static var calendarIsImmutable: EKError.Code}

The calendar is immutable and you can't modify or delete it.

\texttt{static var sourceDoesNotAllowCalendarAddDelete: EKError.Code}

The source doesn't allow you to add or delete calendars.

\texttt{static var recurringReminderRequiresDueDate: EKError.Code}

The recurring reminder requires a due date.

\texttt{static var structuredLocationsNotSupported: EKError.Code}

The source to which this calendar belongs doesn't support structured locations.

\texttt{static var reminderLocationsNotSupported: EKError.Code}

The source doesn't support locations on reminders.

\texttt{static var alarmProximityNotSupported: EKError.Code}

The source doesn't allow geofences on alarms.

\texttt{static var calendarDoesNotAllowEvents: EKError.Code}

The calendar doesn't allow you to add events.

\texttt{static var calendarDoesNotAllowReminders: EKError.Code}

The calendar doesn't allow you to add reminders.

\texttt{static var sourceDoesNotAllowReminders: EKError.Code}

The source doesn't allow calendars supporting reminder entity types.

\texttt{static var sourceDoesNotAllowEvents: EKError.Code}

The source doesn't allow calendars supporting event entity types.

\texttt{static var priorityIsInvalid: EKError.Code}

The priority number for the reminder is invalid.

\texttt{static var invalidEntityType: EKError.Code}

The entity type is invalid.

\texttt{static var procedureAlarmsNotMutable: EKError.Code}

You can't create or modify procedure alarms.

\texttt{static var eventStoreNotAuthorized: EKError.Code}

The user hasn't authorized your app to access events or reminders.

\texttt{static var osNotSupported: EKError.Code}

The action isn't supported on the current operating system.

\texttt{static var invalidInviteReplyCalendar: EKError.Code}

The calendar is invalid or nil.

\texttt{static var notificationsCollectionFlagSet: EKError.Code}

The notification collection doesn't have the notifications collection flag.

\texttt{static var sourceMismatch: EKError.Code}

The object's source doesn't match its container's source.

\texttt{static var notificationCollectionMismatch: EKError.Code}

The notification collection that contains this notification doesn't match the collection the system is trying to save.

\texttt{static var notificationSavedWithoutCollection: EKError.Code}

The notification can't save because you haven't added it to a notification collection and saved the collection first.

\texttt{static var last: EKError.Code}

This error is for internal use.

Error Domain

\texttt{let EKErrorDomain: String}

A string that identifies the EventKit error domain.

Type Properties

\texttt{static var errorDomain: String}

\texttt{static var reminderAlarmContainsEmailOrUrl: EKError.Code}

Relationships

Conforms To

CustomNSError

Equatable

Error

Hashable

Sendable

See Also

Errors

\texttt{enum Code}

Error codes for EventKit errors.

\texttt{let EKErrorDomain: String}

A string that identifies the EventKit error domain.

\newpage
\end{document}