\documentclass{article}
\title{}
\author{}
\date{}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{tabularx}

\begin{document}
EventKit/EKParticipant

Class

\textbf{EKParticipant}

A class that represents person, group, or room invited to a calendar event.

iOS 4.0+ $|$ iPadOS 4.0+ $|$ Mac Catalyst 13.1+ $|$ macOS 10.8+ $|$ visionOS 1.0+ $|$ watchOS 2.0+

\texttt{class EKParticipant}

Overview

Do not create \texttt{EKParticipant} objects directly. Instead, use the property attendees on \texttt{EKCalendarItem} to return an array of \texttt{EKParticipant} objects.

EventKit cannot add participants to an event nor change participant information. Use the properties in this class to get information about a participant.

A participant can be a person, group, room, or other resource.

Topics

Defining Participants

\texttt{enum EKParticipantRole}

The participant's role for an event.

\texttt{enum EKParticipantType}

The type of participant.

\texttt{enum EKParticipantStatus}

The participant's attendance status for an event.

\texttt{enum EKParticipantScheduleStatus}

The participant's scheduled status.

Accessing Participant Properties

\texttt{var isCurrentUser: Bool}

A Boolean value indicating whether this participant represents the owner of this account.

\texttt{var name: String?}

The participant's name.

\texttt{var participantRole: EKParticipantRole}

The participant's role in the event.

\texttt{var participantStatus: EKParticipantStatus}

The participant's attendance status.

\texttt{var participantType: EKParticipantType}

The participant's type.

\texttt{var url: URL}

The URL representing this participant.

\texttt{var contactPredicate: NSPredicate}

A predicate to use with the Contacts framework to retrieve the corresponding contact instance.

Finding Participant Address Book Records

\texttt{func abRecord(with: ABAddressBook) $\rightarrow$ ABRecord?}

Returns the address book record that represents the participant.

\texttt{func abPerson(in: ABAddressBook) $\rightarrow$ ABPerson?}

Returns the address book record that represents the participant.

\textit{Deprecated}

\texttt{typealias ABAddressBook}

A reference to an \texttt{ABAddressBook} object.

\textit{Deprecated}

\texttt{typealias ABRecord}

A reference to an \texttt{ABRecord} object or any of its derivedopaque types.

\textit{Deprecated}

Relationships

Inherits From

\texttt{EKObject}

Conforms To

\texttt{CVarArg}

\texttt{CustomDebugStringConvertible}

\texttt{CustomStringConvertible}

\texttt{Equatable}

\texttt{Hashable}

\texttt{NSCopying}

\texttt{NSObjectProtocol}

See Also

Calendars

\texttt{class EKCalendar}

A class that represents a calendar in EventKit.

\newpage
\end{document}