\documentclass{article}
\title{}
\author{}
\date{}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{tabularx}

\begin{document}
EventKit / EKError / EKError.Code

Enumeration

\textbf{EKError.Code}

Error codes for EventKit errors.

iOS | iPadOS | Mac Catalyst | macOS | visionOS | watchOS

\texttt{enum Code}

\textbf{Topics}

\textbf{Constants}

\texttt{case eventNotMutable}

The event isn't mutable and you can't save or delete it.

\texttt{case noCalendar}

The event isn't associated with a calendar.

\texttt{case noStartDate}

The event has no start date set.

\texttt{case noEndDate}

The event has no end date set.

\texttt{case datesInverted}

The event's end date occurs before its start date.

\texttt{case internalFailure}

An internal error occurred.

\texttt{case calendarReadOnly}

The calendar is read-only and you can't add events to it.

\texttt{case durationGreaterThanRecurrence}

The duration of an event is greater than its recurrence interval.

\texttt{case alarmGreaterThanRecurrence}

The alarm interval is greater than the recurrence interval.

\texttt{case startDateTooFarInFuture}

The start date is further into the future than the calendar can display.

\texttt{case startDateCollidesWithOtherOccurrence}

The event's start date collides with another occurrence of the event.

\texttt{case objectBelongsToDifferentStore}

The object belongs to a different calendar store.

\texttt{case invitesCannotBeMoved}

You can't move the event because it's an invitation.

\texttt{case invalidSpan}

The system encountered an invalid span during a save or deletion.

\texttt{case calendarHasNoSource}

You can't save the calendar without setting a source first.

\texttt{case calendarSourceCannotBeModified}

You can't move the calendar to another source.

\texttt{case calendarIsImmutable}

The calendar is immutable and you can't modify or delete it.

\texttt{case sourceDoesNotAllowCalendarAddDelete}

The source doesn't allow you to add or delete calendars.

\texttt{case recurringReminderRequiresDueDate}

The recurring reminder requires a due date.

\texttt{case structuredLocationsNotSupported}

The source to which this calendar belongs doesn't support structured locations.

\texttt{case reminderLocationsNotSupported}

The source doesn't support locations on reminders.

\texttt{case alarmProximityNotSupported}

The source doesn't allow geofences on alarms.

\texttt{case calendarDoesNotAllowEvents}

The calendar doesn't allow you to add events.

\texttt{case calendarDoesNotAllowReminders}

The calendar doesn't allow you to add reminders.

\texttt{case sourceDoesNotAllowReminders}

The source doesn't allow calendars supporting reminder entity types.

\texttt{case sourceDoesNotAllowEvents}

The source doesn't allow calendars supporting event entity types.

\texttt{case priorityIsInvalid}

The priority number for the reminder is invalid.

\texttt{case invalidEntityType}

The entity type is invalid.

\texttt{case procedureAlarmsNotMutable}

You can't create or modify procedure alarms.

\texttt{case eventStoreNotAuthorized}

The user hasn't authorized your app to access events or reminders.

\texttt{case osNotSupported}

The action isn't supported on the current operating system.

\texttt{case invalidInviteReplyCalendar}

The calendar is invalid or nil.

\texttt{case notificationsCollectionFlagNotSet}

The notification collection doesn't have the notifications collection flag.

\texttt{case sourceMismatch}

The object's source doesn't match its container's source.

\texttt{case notificationCollectionMismatch}

The notification collection that contains this notification doesn't match the collection the system is trying to save.

\texttt{case notificationSavedWithoutCollection}

The notification can't save because you haven't added it to a notification collection and saved the collection first.

\texttt{case last}

This error is for internal use.

\textbf{Enumeration Cases}

\texttt{case reminderAlarmContainsEmail0rUrl}

\textbf{Initializers}

\texttt{init?(rawValue: Int)}

\textbf{Relationships}

\textbf{Conforms To}

BitwiseCopyable

Equatable

Hashable

RawRepresentable

Sendable

\textbf{See Also}

\textbf{Errors}

\texttt{struct EKError}

An EventKit error.

\texttt{let EKErrorDomain: String}

A string that identifies the EventKit error domain.

\newpage
\end{document}