\documentclass{article}
\title{}
\author{}
\date{}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{tabularx}

\begin{document}
EventKit / EKCalendar

Class

\textbf{EKCalendar}

A class that represents a calendar in EventKit.

iOS 4.0+ | iPadOS 4.0+ | Mac Catalyst 13.1+ | macOS 10.8+ | visionOS 1.0+ | watchOS 2.0+

\texttt{@interface EKCalendar : EKObject}

Mentioned in

\texttt{Retrieving events and reminders}

Overview

Use the properties in this class to get attributes about a calendar, such as its title and type. Use the \texttt{calendarForEntityType:eventStore:} method to create a calendar object.

Topics

Creating Calendars

\texttt{+ calendarForEntityType:eventStore:}

Creates a new calendar that can contain the given entity type.

\texttt{+ calendarWithEventStore+}

Creates and returns a calendar belonging to a specified event store.

\textbf{Deprecated}

Accessing Calendar Properties

\texttt{EKCalendarType}

Possible calendar types.

\texttt{EKCalendarEventAvailabilityMask}

A bitmask indicating the event availability settings that the calendar can support.

\texttt{allowsContentModifications}

A Boolean value that indicates whether you can add, edit, and delete items in the calendar.

\texttt{CGColor}

The calendar's color.

\texttt{color}

The calendar's color.

\texttt{immutable}

A Boolean value indicating whether the calendar's properties can be edited or deleted.

\texttt{title}

The calendar's title.

\texttt{type}

The calendar's type.

\texttt{allowedEntityTypes}

The entity types this calendar can contain.

\texttt{source}

The source object representing the account to which this calendar belongs.

\texttt{subscribed}

A Boolean value indicating whether the calendar is a subscribed calendar.

\texttt{supportedEventAvailabilities}

The event availability settings supported by this calendar, as indicated by a bitmask.

\texttt{calendarIdentifier}

A unique identifier for the calendar.

\texttt{DATE\_COMPONENTS\_DO\_NOT\_USE}

A deprecated function.

\textbf{Deprecated}

\texttt{DATE\_COMPONENTS\_DO\_NOT\_USE}

A deprecated function.

\textbf{Deprecated}

Relationships

Inherits From

\texttt{EKObject}

See Also

Calendars

\texttt{EKParticipant}

A class that represents person, group, or room invited to a calendar event.
\newpage
\end{document}