\documentclass{article}
\title{}
\author{}
\date{}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{array}
\usepackage{enumitem}
\usepackage{tabularx}

\begin{document}
Available on iOS 4.0 and later

EventKit / EKRecurrenceDayOfWeek

Class

\textbf{EKRecurrenceDayOfWeek}

A class that represents the day of the week.

iOS 4.0+ | iPadOS 4.0+ | Mac Catalyst 13.1+ | macOS 10.8+ | visionOS 1.0+ | watchOS 2.0+

@interface EKRecurrenceDayOfWeek : NSObject

Mentioned in

Creating a recurring event

Overview

The EKRecurrenceDayOfWeek class represents a day of the week for use with an EKRecurrenceRule object.

A day of the week can optionally have a week number, indicating a specific day in the recurrence rule's frequency. For example, a day of the week with a day value of Tuesday and a week number of 2 would represent the second Tuesday of every month in a monthly recurrence rule, and the second Tuesday of every year in a yearly recurrence rule. A day of the week with a week number of 0 ignores its week number.

Topics

Creating a Day of the Week

\textit{EKWeekday}

The day of the week.

\textit{dayOfWeek:}

Creates and returns a day of the week with a given day.

+ \textit{dayOfWeek: weekNumber:}

Creates and returns an autoreleased day of the week with a given day and week number.

- \textit{initWithDayOfTheWeek: weekNumber:}

Initializes and returns a day of the week with a given day and week number.

Accessing Properties of a Day of the Week

\textit{dayOfTheWeek}

The day of the week.

\textit{weekNumber}

The week number of the day of the week.

Relationships

Inherits From

\textit{NSObject}

Conforms To

\textit{NSCopying, NSSecureCoding}

See Also

Recurrence

Creating a recurring event

Set up an event or reminder that repeats.

\textit{EKRecurrenceEnd}

A class that defines the end of a recurrence rule.

\textit{EKRecurrenceRule}

A class that describes the pattern for a recurring event.

\newpage
\end{document}